%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Indian Institute of Technology} % Organisation
    {Indore, India} % Location
    {Sept 2020 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with a four-person team to develop a CNN model that utilised YOLO as a foundation to improve the accuracy of ambient lighting conditions in the Mobile net architecture.}
        \item {Automated and optimised the data handling process for traffic signs, working with Ubuntu 20.04 did shell scripting, and employed other Linux tools.}
        \item {Significantly boosted the model's accuracy by 60\%, which was yielding an accuracy of 70-78\% under Indian street light. The older models, had an accuracy of 10-15\%.}
        \item {\textbf{Technical Skills:} Python with PyTorch, NumPy, Matplotlib, Pandas, Scikit-learn, C++, Ubuntu Linux, Linux tools, Apt, Scripting, Git.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Intern} % Job title
    {Raja Ramanna Centre for Advanced Technology} % Organisation
    {Indore, India} % Location
    {Apr 2020 - Sept 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build a model with a team of three that works with a Genetic algorithm and is portable for scheduling scenarios may it be a schedule for school, employee time sheet etc.}
        \item {Designed to be flexible to any case with low time complexity compared to the existing models which were only useful in specific scenarios.}
        \item {Produced everything from scratch and published the library on \href{https://pypi.org/project/genetictabler/}{PyPi.}}
        \item {\textbf{Technical Skills:} Python with GeneticAlgorithm, NumPy, Setuptools, Wheel, Twine, Git.}
        \item {\textbf{Soft Skills:} Leadership, Time Management, Communication, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
